{\huge Supplements for: Changes and trends in budburst and leaf flush across Europe and North America} \\A meta-analysis of local adaptation in spring phenology studies

### 2023-09-24 Docs/supplement.Rnw
more edits, fixed plots

% optional: muck with spacing
\topmargin -1.5cm        
\oddsidemargin 0.5cm   
\evensidemargin 0.5cm  % same as oddsidemargin but for left-hand pages
\textwidth 15.59cm
\textheight 21.94cm 
% \renewcommand{\baselinestretch}{1.5} % 1.5 lines between lines
\parindent 0pt		  % sets leading space for paragraphs
% optional: cute, fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LO]{2023}
\fancyhead[RO]{Manuscript}
% more optionals! %
%\usepackage[hyphens]{url} % this wraps my URL versus letting it spill across the page, a bad habit LaTeX has

@@

\begin{figure}[!h] 
    \centering
 \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_ms/gdd_ms.png}
    \caption{Growing Degree Days (GDD)on each day of spring event in relation to provenance latitude and MAT, coded by symbol for species and color for garden with linear fits from hierarchical Bayesian models.}
    \label{figure:gdd}
\end{figure}

\begin{figure}[!h] 
    \centering
 \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/climate_overlap_continent_comparison.png}
    \caption{The closer a garden is to a provenance, the more overlap in temperature. 
Higher extend of climate overlap in European studies.}
    \label{figure:overlap_continent}
\end{figure}

\begin{figure}[!h] 
    \centering
 \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/prov_lat_mat_continent.png}
    \caption{Placeholder.}
    \label{figure:lat_mat_continent}
\end{figure}

\begin{figure}[!h] 
    \centering
 \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/spp_type_continent.png}
    \caption{Placeholder}
    \label{figure:spp_continent}
\end{figure}

\end{document}

>>>>

% optional: muck with spacing
\topmargin -1.5cm        
\oddsidemargin 0.5cm   
\evensidemargin 0.5cm  % same as oddsidemargin but for left-hand pages
\textwidth 15.59cm
\textheight 21.94cm 
% \renewcommand{\baselinestretch}{1.5} % 1.5 lines between lines
\parindent 0pt		  % sets leading space for paragraphs
% optional: cute, fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LO]{2023}
\fancyhead[RO]{Supplement}
\usepackage{setspace}
% Using \doublespacing in the preamble changes the text to double-line spacing
\doublespacing
% more optionals! %
%\usepackage[hyphens]{url} % this wraps my URL versus letting it spill across the page, a bad habit LaTeX has

@@

% \begin{figure}[!h] 
%     \centering
%  \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_ms/gdd_ms.png}
%     \caption{Growing Degree Days (GDD)on each day of spring event in relation to provenance latitude and MAT, coded by symbol for species and color for garden with linear fits from hierarchical Bayesian models.}
%     \label{figure:gdd}
% \end{figure}

% 
% \begin{figure}[!h] 
%     \centering
%  \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/climate_overlap_continent_comparison.png}
%     \caption{The closer a garden is to a provenance, the more overlap in temperature. 
% Higher extend of climate overlap in European studies.}
%     \label{figure:overlap_continent}
% \end{figure}
% 
% \begin{figure}[!h] 
%     \centering
%  \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/prov_lat_mat_continent.png}
%     \caption{Placeholder.}
%     \label{figure:lat_mat_continent}
% \end{figure}
% 
% 
% \begin{figure}[!h] 
%     \centering
%  \includegraphics[width=\textwidth]{..//..//localadaptclim/Docs/figure_supp/spp_type_continent.png}
%     \caption{Placeholder}
%     \label{figure:spp_continent}
% \end{figure}
% 
 \end{document}
